Discrete Quantum Theories and Computing

### 2019-03-25 dissertation.tex
dissertation.lyx Bibliography Sorted...

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{bahasai}
\setotherlanguage{basque}
\setotherlanguage{french}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{portuges}
\setotherlanguage{turkish}
\setotherlanguage{vietnamese}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

\chapter{Further Discussion\label{chap:Further-Discussion}}

@@

\chapter{Conclusion}

>>>>

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{bahasai}
\setotherlanguage{basque}
\setotherlanguage{french}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{portuges}
\setotherlanguage{turkish}
\setotherlanguage{vietnamese}
\usepackage[style=numeric-comp,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

\chapter{Conclusion and Further Discussion\label{chap:Further-Discussion}}

\section{Conclusion}

Before what we can do further based on this thesis, let's summarize
what we have done previously.\todo{Keep writing\ldots}

@@
